Cloud-SAP: Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments

### 2013-09-15 article/article.tex
Add the 'conclusion' section in the article

\section{Summary and conclusion}

>>>>

\section{Summary and conclusion}
Cloud computing emerged as a completely new paradigm for providing users with IT services in a pay-as-you-go manner. As the time goes by, the clients expectations and requirements in terms of providing services with stringent Quality-of-Service requirements have raised and forced Cloud computing scientists to invent and design new solutions capable of satisfying them.

In this paper we gave a brief overview of current cloud providers capabilities with the stress on auto-scaling features. Then we outlined the architecture of Cloud-SAP platform which facilitates autonomic and scalable provisioning of users' applications. The results of the conducted tests indicate that this model has enormous business potential for both cloud providers and clients.

We hope our work will be of a great benefit to computer scientists and engineers involved in designing and building cloud solutions and its outcome will make progress in enlightening new problems in the area of combining autonomous systems and market-oriented cloud federation.

Our future work will concentrate on implementing the proposed solution and testing it in real-world hardware against business use cases.
